Are We Reusing Outdated Code from Stack Overflow?

### 2016-12-05 cloneoverflow-latex/cloneoverflow.tex
Added updates
Updated with license numbers (still wrong, need fixing)

@@

%			c-jdbc & 2.0.2 & - & 16/09/2005 & - & GLGPL 2.1 & \\

@@

%			checkstyle & 5.1 & 7.2  & 23/09/2016 & git & GLGPL 2.1 \& Apache 2.0 & \textit{Cli, Logging and Beanutils} packages are from the Apache Commons project. \\

@@

%			exoportal & ??? & ??? &  & git & GLGPL 3.0 \& proprietary & Too many new projects \\

@@

%			findbugs & 1.3.9 & 3.0.1 & 06/03/2015 & - & GLGPL 2.0 & \\

@@

%			geotools & 2.7-M3 & 16 & 27/09/2016 & git & GLGPL 2.0 & \\

@@

%			heritrix & 1.14.4 & - & 05/06/2013 & - & GLGPL 2.1 & \\
%			hibernate & 4.2.2 & 5.2.3 & 22/09/2016 & git & GLGPL 2.1+ & \\

@@

%			ireport & 3.7.5 & - & 28/05/2014 & - & Affero GLGPL 3.0 & \\
%			itext & 5.0.3 & 5.5.9 & 27/09/2016 & git & Affero GLGPL 3.0 & \\
%			informa & 0.7.0-alpha2 & - & 07/11/2008 & - & GLGPL 2.1 \& Apache Software 1.1 & \\

@@

%			jasperreports & 3.7.4 & 6.3.1 & 27/09/2016 & git & GLGPL 3.0 &  \\

@@

%			jboss (wildfly) & 5.1.0.GA & 11.0.0.Alpha1 & 27/09/2016 & git & GLGPL 2.1 & Renamed to Wildfly. \\
%			jchempaint & 3.0.1 & 3.4 & 01/09/2016 & git & GLGPL 2.1+ &  \\

@@

%			jfreechart & 1.0.13 & 1.5.0 & 29/08/2016 & git & GLGPL 2.0 &   \\

@@

%			jgraphpad & 5.10.0.2 & - & 10/11/2006 & - & GPL   \& GLGPL (derivatives) & \\
%			jgrapht & 0.8.1 & 1.0.1 & 23/09/2016 & git & GLGPL 2.1 \& Eclipse  1.0 & \\

@@

%			jparse & 0.96 & - & 29/07/2004 & - & GLGPL 2.1 & \\

@@

%			shiftone-jrat & 0.6 & 1-beta-1 & 17/11/2007 & svn & GLGPL 2.0 &  \\

@@

We need an appropriate clone classification scheme to meaningfully categorise the selected clone candidates by hand. We started by studying the 8 patterns of cloning from Kapser et al. \cite{Kapser2006}. We use the patterns to classify 697 clone pairs associated with 34 sampled Stack Overflow fragments. This preliminary investigation aims to evaluate the applicability of Kapser's cloning patterns to our study. Using Simian$_{df}$ clone report, fragments are ranked according to (1) frequency, (2) popularity (i.e.~number of associated Qualitas projects), (3) clone size in SLOC, and (4) clone percentage compared to the fragment size. We then picked the top 10 fragments from the 4 groups resulting in 34 Stack Overflow fragments chosen (there were some overlaps). The 34 selected snippets generate 697 clone pairs. Using Kapser's cloning patterns, the 697 clone pairs were categorised into either Customisation or Templating. Clearly Kapser's cloning patterns are too broad for our study and a more suitable and fine-grained classification scheme is needed. We adopted one of Kapser's cloning patterns, boiler-plate code and API/library protocol as category D, and added 6 new categories observed as common cloning patterns from the manual investigation. The seven categories ranging from A--F presented in \Cref{tab:classification_scheme}. Category A is a clone pair that has evidence to be copied from Qualitas to Stack Overflow (by having comments in source code and explanation or links in Stack Overflow post), and vice versa in category A'. Category B is a clone pair that is exactly identical or highly similar but without any attribution of copying. Category C is a clone pair that has information confirming of copying from the same external source. Category D is a clone pair that is either boiler-plate code (e.g.~\verb|equals()| methods, or getters and setters) or IDE-generated (e.g.~GUI initialisation). Category E are clones created by inheriting the same super class or implementing the same interface. They usually share similar overriding methods. The last category, category F, is a false clone pair. They can be either accidentally similar (e.g.~similar try-catch statements) or similar after code normalisation process. Using this classification scheme, we consider clone pairs in category A, A', B, C as true positive, and clone pairs in category D, E, F as false positive.

@@

\begin{table*}
	\centering
	\caption{Classification results of agreed and disagreed clone pairs. S$_u$ denotes a number of unique Stack Overflow snippets. Q$_u$ and Q$_{up}$ denote a number of unique Qualitas Java files and unique Qualitas projects respectively.}
	\label{tab:classification_good_o}
	\small
	\resizebox{2.1\columnwidth}{!}{%
		\begin{tabular}{|l"r|r|r|r|r|r|r|r"r|r|r|r|r|r|r"r|r|r|r|}
			\hline
			Classificaiton & A & A' & B & C & \textbf{Sum} & S$_{u}$ & Q$_u$ & Q$_{up}$ & D  & E & F & \textbf{Sum} & S$_{u}$ & Q$_u$ & Q$_{up}$ & \textbf{Total}  & S$_{u}$ & Q$_u$ & Q$_{up}$\\ 
			\hline 
			\hline
			\multirow{1}{*}{\textit{good-match(0.7)}}  & 1 & 0 & 4  & 3 & \textbf{8} & 7 & 6 & 6 & 58  & 6 & 2189 & \textbf{2253} & 81 & 693 & 58 & \textbf{2261} & 87 & 699 & 59 \\
			\multirow{1}{*}{\textit{ok-match(0.7)}}  & 8 & 0 & 29  & 10 & \textbf{47} & 12 & 14 & 10 & 9158 & 35 & 82 & \textbf{9275} & 100 & 204 & 30 & \textbf{9322} & 112 & 218 & 35 \\
			\hline 
			\hline 
			\multirow{1}{*}{\textit{Simian$_{df}$}} & 19 & 0 & 336 & 17 & \textbf{432} & 148 & 229 & 38 & 209 & 63 & 167 & \textbf{439} & 136 & 214 & 49 & \textbf{871} & 271 & 428 & 58 \\
			\hline
			\multirow{1}{*}{\textit{NiCad$_{df}$}} & 8  & 0 & 27 & 1 & \textbf{36} & 16 & 15 & 5 & 77 & 3 & 82 & \textbf{132} & 52 & 55 & 17 & \textbf{168} & 67 & 69 & 19 \\ 
			\hline
		\end{tabular} 
	}
\end{table*}

@@

\begin{table}
	\centering
	\caption{14 Qualitas projects with the highest number of true clones on Stack Overflow with their respective licenses}
	\label{t:new_and_old}
	%	\resizebox{\columnwidth}{!}{%
	\small
	\begin{tabular}{l|r|p{4cm}}
		\hline 
		Project & Version & Licenses (no.~of files) \\
		\hline
		%		apache-ant & 1.8.4 & Apache2.0 \\
		%		apache-log4j & 1.2.16 & \\
		aspectj & 1.6.9 & Apache-1.1 (182), CPLv1 (3), \newline EPLv1 (2011), None (23), \newline SeeFile (6), Unknown (286) \\
		\hline
		eclipse-SDK &  4.1 & Apache-2 (2183), \newline BSD3NoWarranty (107), \newline CDDLorGPLv2 (296), \newline EPLv1 (18823), MPLv1.1 (93), \newline None (224), SeeFile (8), \newline spdxBSD3 (185), \newline spdxMIT (1), Unknown (714) \\
		\hline
		hadoop & 1.0.0 & Apache-2 (1,935), \newline spxdBSD/Apache-2 (8) \newline None (33), Unknown (14) \\
		\hline
		hibernate & 4.2.2 & Apache-2 (20), \newline GLGPLv2.1+ (31) \newline PublicDomain (1), \newline None (1,850), SeeFile (4), \newline Unknown (4,324) \\
		\hline
		jasperreports & 3.7.4 & GLGPLv2.1+ (3), \newline GLGPLv3+ (1,581), \newline None (1), Unknown (4)\\
		\hline
		jfreechart & 1.0.13 & GLGPLv2.1+ (989) \\
		\hline
		jgraph & 5.13.0.0 & GLGPLv2.1+ (4), \newline spdxBSD (2), Unknown (151), \newline None (24), SeeFile (9) \\
		\hline
		%		jgrapht & 0.8.1 & GLGPL 2.1 \& Eclipse  1.0 \\
		jstock & 1.0.7c & GLGPLv2.1+ (1), \newline GPLv2+ (239), \newline Apache-2 (1), BSD3 (1), \newline None (23), SeeFile (1), \newline spdxMIT (3), Unknown (5)\\
		\hline
		jung2 & 2-0-1 & N/A \\
		\hline
		junit & 4.11 & None (160), Unknown (4)  \\
		\hline
		poi & 3.6 & Apache-2 (2,002), None (5) \\
		\hline
		spring & 3.0.5 & Apache-2 (2,982) \\
		\hline
		struts2 & 2.2.1-all & Apache-2 (1,717), \newline spdxBSD3 (6), \newline None (118), SeeFile (1), \newline Unknown (2) \\
		\hline
		tomcat & 7.0.2 & Apache-2 (1,313), None (11) \\
		%		weka & 3-7-9 & \\
		\hline
	\end{tabular} %
	%	}
\end{table}

@@

\begin{figure*}
	\begin{lstlisting}
/* Code in Stack Overflow #23520731 */     /* SchemaUpdate.java (2016-09-26) */
public void execute (Target target) {      public void execute(EnumSet<TargetType> targetTypes, 
  LOG.runningHbm2ddlSchemaUpdate();                        Metadata metadata, ServiceRegistry serviceRegistry) {
  Connection connection = null;              if ( targetTypes.isEmpty() ) {
  Statement stmt = null;                       LOG.debug(""Skipping SchemaExport as no targets were specified"");
  Writer outputFileWriter = null;              return;
  exceptions.clear();                        }
  try {                                      exceptions.clear();
    DatabaseMetadata meta;                   LOG.runningHbm2ddlSchemaUpdate();
    ...                                      ...
	\end{lstlisting}
	\caption{Outdated code fragment on Stack Overflow post 23520731 copied from SchemaUpdate.java and its latest version in hibernate code base with heavy modifications}
	\label{fig:hibernate_outdated_code}
\end{figure*}

@@

%	\resizebox{2.1\columnwidth}{!}{%
	\begin{tabular}{r|l|p{4.5cm}|r|r|l|l|c|l}

@@

		No. & Project & File & Start & End & License & SO No. & $C$ & C$_{\textit{\textrm{date}}}$ \\

@@

			1 & aspectj-1.6.9  & aspectjtools/../Agent.java  & 7 & 18 & -- & 18303692 & $M$  & 2015-09-08 \\
			2 & aspectj-1.6.9  & aspectjweaver/../Agent.java  & 7 & 18 & -- & 18303692 & $M$  & 2015-09-08 \\
			3 & eclipse-SDK  & GenerateToStringAction.java  & 113 & 166 & EPLv1 & 2513183 & $M$  &  2015-03-17 \\
			4 & eclipse-SDK  & GenerateToStringAction.java  & 117 & 126 & EPLv1  &  2513183	 & $M$  &  2015-03-17 \\
			5 & eclipse-SDK  & GenerateToStringAction.java  & 143 & 165 & EPLv1  &  2513183	 & $M$  &  2015-03-17 \\
			6 & eclipse-SDK  & GenerateToStringAction.java  & 178 & 187 & EPLv1  &  2513183	 & $M$  & 2011-03-01 \\
			7 & eclipse-SDK  & WizardDialog.java  & 377 & 394 & EPLv1  &   11861598	 & $M$  &  2011-02-03 \\
			8 & hadoop-1.0.0  & DBCountPageView.java  & 275 & 287 & Apache-2 & 21702608 & $M$  & 2011-06-12 \\
			9 & hadoop-1.0.0  & DBCountPageView.java  & 289 & 309 & Apache-2 & 21702608 & $M$  & 2011-06-12 \\
			10 & hadoop-1.0.0  & JobSubmissionFiles.java  & 46 & 55 & Apache-2 & 14845581 & $M$  & 2012-06-25 \\
			11 & hadoop-1.0.0  & mapred/../LineRecordReader.java  & 47 & 60 & Apache-2 & 16180910 & $M$  & 2011-07-25 \\
			12 & hadoop-1.0.0  & mapreduce/../LineRecordReader.java  & 75 & 99 & Apache-2 & 16180910 & $M$  & 2011-07-25 \\
			13 & hadoop-1.0.0  & StringUtils.java  & 40 & 56 & Apache-2 & 801987 & $M$  & 2013-02-04 \\
			14 & hadoop-1.0.0  & TestJobCounters.java  & 186 & 192 & Apache-2 & 18833798 & $M$  & 2011-06-12 \\
			15 & hadoop-1.0.0  & TextOutputFormat.java  & 75 & 99 & Apache-2 & 16928749 & $M$  & 2011-06-12 \\
			16 & hadoop-1.0.0  & WritableComparator.java  & 44 & 54 & Apache-2 & 22315734 & $M$  & 2014-11-20 \\
			17 & hibernate-4.2.2  & ConnectionProviderInitiator.java  & 65 & 93 & -- & 15168494 & $M$  & 2012-06-24 \\
			18 & hibernate-4.2.2  & Example.java  & 224 & 243 & -- & 24924255 & $M$  & 2013-04-23 \\
			19 & hibernate-4.2.2  & SchemaUpdate.java  & 115 & 168 & -- & 23520731 & $M$  & 2016-02-05 \\
			20 & hibernate-4.2.2  & SettingsFactory.java  & 244 & 255 & -- & 8257554 & $D$  & 2011-03-11 \\
			21 & hibernate-4.2.2  & SQLServer2005LimitHandler.java  & 43 & 61 & -- & 23967852 & $M$  & 2015-03-12 \\
			22 & jasperreports-3.7.4  & JRVerifier.java  & 982 & 998 & GLGPLv3+ & 8037824 & $M$  & 2008-04-17 \\
			23 & jasperreports-3.7.4  & JRVerifier.java  & 1221 & 1240 & GLGPLv3+ & 8037824 & $M$  & 2011-05-20 \\
			24 & jfreechart-1.0.13  & AbstractXYItemRenderer.java  & 532 & 569 & GLGPLv2.1+ & 12936580 & $M$  & 2016-02-19 \\
			25 & jfreechart-1.0.13  & KeyToGroupMap.java  & 18 & 30 & GLGPLv2.1+ & 16058183 & $M$  & 2013-07-03 \\
			26 & jfreechart-1.0.13  & SpiderWebPlot.java  & 502 & 520 & GLGPLv2.1+ & 21998949 & $M$  & 2008-06-02 \\
			27 & jfreechart-1.0.13  & SpiderWebPlot.java  & 522 & 536 & GLGPLv2.1+ & 21998949 & $M$  & 2008-06-02 \\
			28 & jgraph-5.13.0.0  & HelloWorld.java  & 16 & 22 & GLGPLv2.1+ & 6722760 & $R$  & 2014-04-13 \\
			29 & jgraph-5.13.0.0  & HelloWorld.java  & 28 & 40 & GLGPLv2.1+ & 6722760 & $R$  & 2014-04-13 \\
			30 & jgraph-5.13.0.0  & HelloWorld.java  & 31 & 36 & GLGPLv2.1+ & 6722760 & $R$  & 2014-04-13 \\
			31 & jgraph-5.13.0.0  & HelloWorld.java  & 39 & 56 & GLGPLv2.1+ & 6722760 & $R$  & 2014-04-13 \\
			32 & jstock-1.0.7c  & GoogleMail.java  & 18 & 42 & GPLv2+ & 14940863 & $M$  & 2015-12-13 \\
			33 & jstock-1.0.7c  & GoogleMail.java  & 18 & 42 & GPLv2+ & 24680923 & $M$  & 2015-12-13 \\
			34 & jung2-2\_0\_1  & ShortestPathDemo.java  & 106 & 117 & -- & 6025026 & $M$  & 2010-04-13 \\
			35 & jung2-2\_0\_1  & ShortestPathDemo.java  & 158 & 172 & -- & 6025026 & $M$  & 2010-04-13 \\
			36 & junit-4  & Assert.java  & 33 & 52 & -- & 23586872 & $M$  & 2015-05-12 \\
			37 & junit-4  & ExternalResource.java  & 4 & 23 & -- & 7504040 & $M$  & 2016-06-25 \\
			38 & junit-4.11  & ExpectException.java  & 11 & 29 & -- & 8802082 & $M$  & 2014-05-26 \\
			39 & poi-3.6  & WorkbookFactory.java  & 18 & 28 & Apache-2 & 12593810 & $M$  & 2015-04-29 \\
			40 & spring-3.0.5  & AnnotationMethodHandler \newline ExceptionResolver.java  & 224 & 233 & Apache-2 & 5660519 & $D$  & 2012-01-20 \\
			41 & spring-3.0.5  & AutowireUtils.java  & 32 & 42 & Apache-2 & 20913543 & $M$  & 2014-10-28 \\
			42 & spring-3.0.5  & CustomCollectionEditor.java  & 33 & 71 & Apache-2 & 18623736 & $M$  & 2013-11-21 \\
			43 & spring-3.0.5  & DefaultAnnotation \newline HandlerMapping.java  & 78 & 92 & Apache-2 & 3758110 & $D$  & 2012-01-20 \\
			44 & spring-3.0.5  & DefaultPropertiesPersister.java  & 69 & 80 & Apache-2 & 6149818 & $M$  & 2013-03-19 \\
			45 & spring-3.0.5  & org.springframework.test/../ \newline DelegatingServletInputStream.java  & 6 & 20 & Apache-2 & 20996373 & $M$  & 2016-07-15 \\
			46 & spring-3.0.5  & org.springframework.web/../ \newline DelegatingServletInputStream.java  & 6 & 20 & Apache-2 & 20996373 & $M$  & 2008-12-18 \\
			47 & spring-3.0.5  & org.springframework.web.servlet/../ \newline DelegatingServletInputStream.java  & 6 & 20 & Apache-2 & 20996373 & $M$  & 2008-12-18 \\
			48 & spring-3.0.5  & DispatcherServlet.java  & 91 & 103 & Apache-2 & 4781746 & $M$  & 2011-08-08 \\

>>>>

\FIXME{Can we say the inspected clone set is another benchmark?}

@@

%			c-jdbc & 2.0.2 & - & 16/09/2005 & - & LGPL 2.1 & \\

@@

%			checkstyle & 5.1 & 7.2  & 23/09/2016 & git & LGPL 2.1 \& Apache 2.0 & \textit{Cli, Logging and Beanutils} packages are from the Apache Commons project. \\

@@

%			exoportal & ??? & ??? &  & git & LGPL 3.0 \& proprietary & Too many new projects \\

@@

%			findbugs & 1.3.9 & 3.0.1 & 06/03/2015 & - & LGPL 2.0 & \\

@@

%			geotools & 2.7-M3 & 16 & 27/09/2016 & git & LGPL 2.0 & \\

@@

%			heritrix & 1.14.4 & - & 05/06/2013 & - & LGPL 2.1 & \\
%			hibernate & 4.2.2 & 5.2.3 & 22/09/2016 & git & LGPL 2.1+ & \\

@@

%			ireport & 3.7.5 & - & 28/05/2014 & - & Affero LGPL 3.0 & \\
%			itext & 5.0.3 & 5.5.9 & 27/09/2016 & git & Affero LGPL 3.0 & \\
%			informa & 0.7.0-alpha2 & - & 07/11/2008 & - & LGPL 2.1 \& Apache Software 1.1 & \\

@@

%			jasperreports & 3.7.4 & 6.3.1 & 27/09/2016 & git & LGPL 3.0 &  \\

@@

%			jboss (wildfly) & 5.1.0.GA & 11.0.0.Alpha1 & 27/09/2016 & git & LGPL 2.1 & Renamed to Wildfly. \\
%			jchempaint & 3.0.1 & 3.4 & 01/09/2016 & git & LGPL 2.1+ &  \\

@@

%			jfreechart & 1.0.13 & 1.5.0 & 29/08/2016 & git & LGPL 2.0 &   \\

@@

%			jgraphpad & 5.10.0.2 & - & 10/11/2006 & - & GPL   \& LGPL (derivatives) & \\
%			jgrapht & 0.8.1 & 1.0.1 & 23/09/2016 & git & LGPL 2.1 \& Eclipse  1.0 & \\

@@

%			jparse & 0.96 & - & 29/07/2004 & - & LGPL 2.1 & \\

@@

%			shiftone-jrat & 0.6 & 1-beta-1 & 17/11/2007 & svn & LGPL 2.0 &  \\

@@

We need an appropriate clone classification scheme to meaningfully categorise the selected clone candidates by hand. We started by studying the 8 patterns of cloning from Kapser et al. \cite{Kapser2006,Kapser2008}. We use the patterns to classify 697 clone pairs associated with 34 sampled Stack Overflow fragments. This preliminary investigation aims to evaluate the applicability of Kapser's cloning patterns to our study. Using Simian$_{df}$ clone report, fragments are ranked according to (1) frequency, (2) popularity (i.e.~number of associated Qualitas projects), (3) clone size in SLOC, and (4) clone percentage compared to the fragment size. We then picked the top 10 fragments from the 4 groups resulting in 34 Stack Overflow fragments chosen (there were some overlaps). The 34 selected snippets generate 697 clone pairs. Using Kapser's cloning patterns, the 697 clone pairs were categorised into either Customisation or Templating. Clearly Kapser's cloning patterns are too broad for our study and a more suitable and fine-grained classification scheme is needed. We adopted one of Kapser's cloning patterns, boiler-plate code and API/library protocol as category D, and added 6 new categories observed as common cloning patterns from the manual investigation. The seven categories ranging from A--F presented in \Cref{tab:classification_scheme}. Category A is a clone pair that has evidence to be copied from Qualitas to Stack Overflow (by having comments in source code and explanation or links in Stack Overflow post), and vice versa in category A'. Category B is a clone pair that is exactly identical or highly similar but without any attribution of copying. Category C is a clone pair that has information confirming of copying from the same external source. Category D is a clone pair that is either boiler-plate code (e.g.~\verb|equals()| methods, or getters and setters) or IDE-generated (e.g.~GUI initialisation). Category E are clones created by inheriting the same super class or implementing the same interface. They usually share similar overriding methods. The last category, category F, is a false clone pair. They can be either accidentally similar (e.g.~similar try-catch statements) or similar after code normalisation process. Using this classification scheme, we consider clone pairs in category A, A', B, C as true positive, and clone pairs in category D, E, F as false positive.

@@

\begin{table*}
	\centering
	\caption{Classification results of agreed and disagreed clone pairs. S$_u$ denotes a number of unique Stack Overflow snippets. Q$_u$ and Q$_{up}$ denote a number of unique Qualitas Java files and unique Qualitas projects respectively.}
	\label{tab:classification_good_o}
	\small
	\resizebox{2.1\columnwidth}{!}{%
		\begin{tabular}{|l"r|r|r|r|r|r|r|r"r|r|r|r|r|r|r"r|r|r|r|}
			\hline
			Classificaiton & A & A' & B & C & \textbf{Sum} & S$_{u}$ & Q$_u$ & Q$_{up}$ & D  & E & F & \textbf{Sum} & S$_{u}$ & Q$_u$ & Q$_{up}$ & \textbf{Total}  & S$_{u}$ & Q$_u$ & Q$_{up}$\\ 
			\hline 
			\hline
			\multirow{1}{*}{\textit{good-match(0.7)}}  & 1 & 0 & 4  & 3 & \textbf{8} & 7 & 6 & 6 & 58  & 6 & 2189 & \textbf{2253} & 81 & 693 & 58 & \textbf{2261} & 87 & 699 & 59 \\
			\multirow{1}{*}{\textit{ok-match(0.7)}}  & 8 & 0 & 29  & 10 & \textbf{47} & 12 & 14 & 10 & 9158 & 35 & 82 & \textbf{9275} & 100 & 204 & 30 & \textbf{9322} & 112 & 218 & 35 \\
			\hline 
			\hline 
			\multirow{1}{*}{\textit{Simian$_{df}$}} & 79 & 0 & 336 & 17 & \textbf{432} & 148 & 229 & 38 & 209 & 63 & 167 & \textbf{439} & 136 & 214 & 49 & \textbf{871} & 271 & 428 & 58 \\
			\hline
			\multirow{1}{*}{\textit{NiCad$_{df}$}} & 8  & 0 & 27 & 1 & \textbf{36} & 16 & 15 & 5 & 77 & 3 & 82 & \textbf{132} & 52 & 55 & 17 & \textbf{168} & 67 & 69 & 19 \\ 
			\hline
		\end{tabular} 
	}
\end{table*}

@@

\begin{table}
	\centering
	\caption{14 Qualitas projects with the highest number of true clones on Stack Overflow with their respective licenses}
	\label{t:q_projects_license}
	%	\resizebox{\columnwidth}{!}{%
	\small
	\begin{tabular}{l|r|p{4cm}}
		\hline 
		Project & Version & Licenses (no.~of files) \\
		\hline
		%		apache-ant & 1.8.4 & Apache2.0 \\
		%		apache-log4j & 1.2.16 & \\
		aspectj & 1.6.9 & Apache-1.1 (182), CPLv1 (3), \newline EPLv1 (2011), None (23), \newline SeeFile (6), Unknown (286) \\
		\hline
		eclipse-SDK &  4.1 & Apache-2 (2183), \newline BSD3NoWarranty (107), \newline CDDLorGPLv2 (296), \newline EPLv1 (18823), MPLv1.1 (93), \newline None (224), SeeFile (8), \newline spdxBSD3 (185), \newline spdxMIT (1), Unknown (714) \\
		\hline
		hadoop & 1.0.0 & Apache-2 (1,935), \newline spxdBSD/Apache-2 (8) \newline None (33), Unknown (14) \\
		\hline
		hibernate & 4.2.2 & Apache-2 (20), \newline LGPLv2.1+ (31) \newline PublicDomain (1), \newline None (1,850), SeeFile (4), \newline Unknown (4,324) \\
		\hline
		jasperreports & 3.7.4 & LGPLv2.1+ (3), \newline LGPLv3+ (1,581), \newline None (1), Unknown (4)\\
		\hline
		jfreechart & 1.0.13 & LGPLv2.1+ (989) \\
		\hline
		jgraph & 5.13.0.0 & LGPLv2.1+ (4), \newline spdxBSD (2), Unknown (151), \newline None (24), SeeFile (9) \\
		\hline
		%		jgrapht & 0.8.1 & LGPL 2.1 \& Eclipse  1.0 \\
		jstock & 1.0.7c & LGPLv2.1+ (1), \newline GPLv2+ (239), \newline Apache-2 (1), BSD3 (1), \newline None (23), SeeFile (1), \newline spdxMIT (3), Unknown (5)\\
		\hline
		jung2 & 2-0-1 & N/A \\
		\hline
		junit & 4.11 & None (160), Unknown (4)  \\
		\hline
		poi & 3.6 & Apache-2 (2,002), None (5) \\
		\hline
		spring & 3.0.5 & Apache-2 (2,982) \\
		\hline
		struts2 & 2.2.1-all & Apache-2 (1,717), \newline spdxBSD3 (6), \newline None (118), SeeFile (1), \newline Unknown (2) \\
		\hline
		tomcat & 7.0.2 & Apache-2 (1,313), None (11) \\
		%		weka & 3-7-9 & \\
		\hline
	\end{tabular} %
	%	}
\end{table}

@@

\begin{figure*}
	\begin{lstlisting}
/* Code in Stack Overflow #23520731 */     /* SchemaUpdate.java (2016-09-26) */
public void execute (Target target) {      public void execute(EnumSet<TargetType> targetTypes, 
  LOG.runningHbm2ddlSchemaUpdate();                        Metadata metadata, ServiceRegistry serviceRegistry) {
  Connection connection = null;              if ( targetTypes.isEmpty() ) {
  Statement stmt = null;                       LOG.debug(""Skipping SchemaExport as no targets were specified"");
  Writer outputFileWriter = null;              return;
  exceptions.clear();                        }
  try {                                      exceptions.clear();
    DatabaseMetadata meta;                   LOG.runningHbm2ddlSchemaUpdate();
    ...                                      ...
	\end{lstlisting}
	\caption{Outdated code fragment on Stack Overflow post 23520731. This code has been copied from SchemaUpdate.java and its latest version in hibernate code base contains several modifications.}
	\label{fig:hibernate_outdated_code}
\end{figure*}

@@

	\resizebox{2.1\columnwidth}{!}{%
	\begin{tabular}{r|l|p{4.5cm}|r|r|l|l|l|c|l}

@@

		No. & Project & File & Start & End & License & SO Post & License & $C$ & C$_{\textit{\textrm{date}}}$ \\

@@

			1 & aspectj-1.6.9  & aspectjtools/../Agent.java  & 7 & 18 & -- & 18303692 & -- & $M$  & 2015-09-08 \\
			2 & aspectj-1.6.9  & aspectjweaver/../Agent.java  & 7 & 18 & -- & 18303692 & & $M$  & 2015-09-08 \\
			3 & eclipse-SDK  & GenerateToStringAction.java  & 113 & 166 & EPLv1 & 2513183 & EPLv1 & $M$  &  2015-03-17 \\
			4 & eclipse-SDK  & GenerateToStringAction.java  & 117 & 126 & EPLv1  &  2513183	& EPLv1 & $M$  &  2015-03-17 \\
			5 & eclipse-SDK  & GenerateToStringAction.java  & 143 & 165 & EPLv1  &  2513183	& EPLv1 & $M$  &  2015-03-17 \\
			6 & eclipse-SDK  & GenerateToStringAction.java  & 178 & 187 & EPLv1  &  2513183	& EPLv1 & $M$  & 2011-03-01 \\
			7 & eclipse-SDK  & WizardDialog.java  & 377 & 394 & EPLv1  &   11861598	& -- & $M$  &  2011-02-03 \\
			8 & hadoop-1.0.0  & DBCountPageView.java  & 275 & 287 & Apache-2 & 21702608 & -- & $M$  & 2011-06-12 \\
			9 & hadoop-1.0.0  & DBCountPageView.java  & 289 & 309 & Apache-2 & 21702608 & -- & $M$  & 2011-06-12 \\
			10 & hadoop-1.0.0  & JobSubmissionFiles.java  & 46 & 55 & Apache-2 & 14845581 & -- & $M$  & 2012-06-25 \\
			11 & hadoop-1.0.0  & mapred/../LineRecordReader.java  & 47 & 60 & Apache-2 & 16180910 & -- & $M$  & 2011-07-25 \\
			12 & hadoop-1.0.0  & mapreduce/../LineRecordReader.java  & 75 & 99 & Apache-2 & 16180910 & -- & $M$  & 2011-07-25 \\
			13 & hadoop-1.0.0  & StringUtils.java  & 40 & 56 & Apache-2 & 801987 & -- & $M$  & 2013-02-04 \\
			14 & hadoop-1.0.0  & TestJobCounters.java  & 186 & 192 & Apache-2 & 18833798 & -- & $M$  & 2011-06-12 \\
			15 & hadoop-1.0.0  & TextOutputFormat.java  & 75 & 99 & Apache-2 & 16928749 & -- & $M$  & 2011-06-12 \\
			16 & hadoop-1.0.0  & WritableComparator.java  & 44 & 54 & Apache-2 & 22315734 & -- & $M$  & 2014-11-20 \\
			17 & hibernate-4.2.2  & ConnectionProviderInitiator.java  & 65 & 93 & -- & 15168494 & -- & $M$  & 2012-06-24 \\
			18 & hibernate-4.2.2  & Example.java  & 224 & 243 & -- & 24924255 & -- & $M$  & 2013-04-23 \\
			19 & hibernate-4.2.2  & SchemaUpdate.java  & 115 & 168 & -- & 23520731 & -- & $M$  & 2016-02-05 \\
			20 & hibernate-4.2.2  & SettingsFactory.java  & 244 & 255 & -- & 8257554 & -- & $D$  & 2011-03-11 \\
			21 & hibernate-4.2.2  & SQLServer2005LimitHandler.java  & 43 & 61 & -- & 23967852 & -- & $M$  & 2015-03-12 \\
			22 & jasperreports-3.7.4  & JRVerifier.java  & 982 & 998 & LGPLv3+ & 8037824 & -- & $M$  & 2008-04-17 \\
			23 & jasperreports-3.7.4  & JRVerifier.java  & 1221 & 1240 & LGPLv3+ & 8037824 & -- & $M$  & 2011-05-20 \\
			24 & jfreechart-1.0.13  & AbstractXYItemRenderer.java  & 532 & 569 & LGPLv2.1+ & 12936580 & -- & $M$  & 2016-02-19 \\
			25 & jfreechart-1.0.13  & KeyToGroupMap.java  & 18 & 30 & LGPLv2.1+ & 16058183 & -- & $M$  & 2013-07-03 \\
			26 & jfreechart-1.0.13  & SpiderWebPlot.java  & 502 & 520 & LGPLv2.1+ & 21998949 & -- & $M$  & 2008-06-02 \\
			27 & jfreechart-1.0.13  & SpiderWebPlot.java  & 522 & 536 & LGPLv2.1+ & 21998949 & -- & $M$  & 2008-06-02 \\
			28 & jgraph-5.13.0.0  & HelloWorld.java  & 16 & 22 & LGPLv2.1+ & 6722760 & -- & $R$  & 2014-04-13 \\
			29 & jgraph-5.13.0.0  & HelloWorld.java  & 28 & 40 & LGPLv2.1+ & 6722760 & -- & $R$  & 2014-04-13 \\
			30 & jgraph-5.13.0.0  & HelloWorld.java  & 31 & 36 & LGPLv2.1+ & 6722760 & -- & $R$  & 2014-04-13 \\
			31 & jgraph-5.13.0.0  & HelloWorld.java  & 39 & 56 & LGPLv2.1+ & 6722760 & -- & $R$  & 2014-04-13 \\
			32 & jstock-1.0.7c  & GoogleMail.java  & 18 & 42 & GPLv2+ & 14940863 & -- & $M$  & 2015-12-13 \\
			33 & jstock-1.0.7c  & GoogleMail.java  & 18 & 42 & GPLv2+ & 24680923 & -- & $M$  & 2015-12-13 \\
			34 & jung2-2\_0\_1  & ShortestPathDemo.java  & 106 & 117 & -- & 6025026 & -- & $M$  & 2010-04-13 \\
			35 & jung2-2\_0\_1  & ShortestPathDemo.java  & 158 & 172 & -- & 6025026 & -- & $M$  & 2010-04-13 \\
			36 & junit-4  & Assert.java  & 33 & 52 & -- & 23586872 & -- & $M$  & 2015-05-12 \\
			37 & junit-4  & ExternalResource.java  & 4 & 23 & -- & 7504040 & -- & $M$  & 2016-06-25 \\
			38 & junit-4.11  & ExpectException.java  & 11 & 29 & -- & 8802082 & -- & $M$  & 2014-05-26 \\
			39 & poi-3.6  & WorkbookFactory.java  & 18 & 28 & Apache-2 & 12593810 & -- & $M$  & 2015-04-29 \\
			40 & spring-3.0.5  & AnnotationMethodHandler \newline ExceptionResolver.java  & 224 & 233 & Apache-2 & 5660519 & -- & $D$  & 2012-01-20 \\
			41 & spring-3.0.5  & AutowireUtils.java  & 32 & 42 & Apache-2 & 20913543 & -- & $M$  & 2014-10-28 \\
			42 & spring-3.0.5  & CustomCollectionEditor.java  & 33 & 71 & Apache-2 & 18623736 & -- & $M$  & 2013-11-21 \\
			43 & spring-3.0.5  & DefaultAnnotation \newline HandlerMapping.java  & 78 & 92 & Apache-2 & 3758110 & -- & $D$  & 2012-01-20 \\
			44 & spring-3.0.5  & DefaultPropertiesPersister.java  & 69 & 80 & Apache-2 & 6149818 & -- & $M$  & 2013-03-19 \\
			45 & spring-3.0.5  & org.springframework.test/../ \newline DelegatingServletInputStream.java  & 6 & 20 & Apache-2 & 20996373 & -- & $M$  & 2016-07-15 \\
			46 & spring-3.0.5  & org.springframework.web/../ \newline DelegatingServletInputStream.java  & 6 & 20 & Apache-2 & 20996373 & -- & $M$  & 2008-12-18 \\
